### 2019-12-17 ic-journal/multivariate.tex
Expanded the rest three "w.r.t."

Another important property of contexts is their composability: if we
substitute some free variables in a context with some other contexts, the
resulting term is still a valid context (w.r.t.~the same set of variables):
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[context_combin]}
\end{alltt}

Not every term within the CCS syntax is a context, as
context (or equation) variables are not allowed to occur within recursion. The converse
holds however: if the set of free variables of a CCS term
is disjoint from a list of variables, then the term is indeed a context
\hl{with respect to} such list of variables:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint_imp_context]}
\end{alltt}
On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context_rec]}
\end{alltt}
In the above lemma we cannot
conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
because $Y$ may appear in both sets.
We also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
the bound variable $Y$ may occur freely within another nested
recursion. For instance, variable $Y$ is free
in $\recu Y E$ , for $E = \recu Z (a.Y + b.Z) + c.Y$.

For weakly guarded contexts, % (which are also normal contexts),
besides their usual properties as in the \univariate case (i.e., weak
guardedness, \HOLinline{\HOLConst{WG}}), we also need
their composability \hl{with respect to}~\multivariate contexts: if we
substitute some free variables in a context $C$ with some weakly guarded
contexts, the resulting context is weakly guarded (w.r.t.~the same set of variables):
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[weakly_guarded_combin]}
\end{alltt}

>>>>

Another important property of contexts is their composability: if we
substitute some free variables in a context with some other contexts, the
resulting term is still a valid context (\hl{with respect to} the same set of variables):
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLConst{context} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[context_combin]}
\end{alltt}

Not every term within the CCS syntax is a context, as
context (or equation) variables are not allowed to occur within recursion. The converse
holds however: if the set of free variables of a CCS term
is disjoint from a list of variables, then the term is indeed a context
\hl{with respect to} such list of variables:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint_imp_context]}
\end{alltt}
On the other hand, for any context (\hl{with respect to} $\til X$) of the form $\recu Y E$,
the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context_rec]}
\end{alltt}
In the above lemma we cannot
conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}},
because $Y$ may appear in both sets.
We also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
the bound variable $Y$ may occur freely within another nested
recursion. For instance, variable $Y$ is free
in $\recu Y E$ , for $E = \recu Z (a.Y + b.Z) + c.Y$.

For weakly guarded contexts, % (which are also normal contexts),
besides their usual properties as in the \univariate case (i.e., weak
guardedness, \HOLinline{\HOLConst{WG}}), we also need
their composability \hl{with respect to}~\multivariate contexts: if we
substitute some free variables in a context $C$ with some weakly guarded
contexts, the resulting context is weakly guarded (\hl{with respect to} the same set of variables):
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
   \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \ensuremath{(}\ensuremath{[}\HOLFreeVar{Es}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{C}\ensuremath{)}\hfill{[weakly_guarded_combin]}
\end{alltt}
